---
title: "Analysis of an example dataset"
date: "`r format(Sys.time(), '%Y - %m - %d')`"
output: 
  html_document:
    toc: true
    toc_float:
      toc_collapsed: false
    theme: flatly
vignette: >
  %\VignetteEngine{knitr::knitr}
  %\VignetteIndexEntry{Analysis of an example dataset}
  %\usepackage[UTF-8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Input data format

The input file can be of many types as long as it can be converted to a `data.frame` containing a number of columns with protein intensities and one column with protein identifiers. A protein identifier correspond to a unique entry in the UniProt database. Multiple protein identifiers can be associated with a single protein group.

## Load data
Load an example dataset containing protein group intensities:

```{r message=FALSE, warning=FALSE}
library(InteRact)
data("proteinGroups_Cbl")
names(proteinGroups_Cbl)[1:20]
```

## Map conditions

Protein intensity column names start with "Intensity" :

```{r message=FALSE, warning=FALSE}
idx_intensity_columns <- grep("^Intensity.", names(proteinGroups_Cbl))
print(names(proteinGroups_Cbl)[idx_intensity_columns][1:10])
```

Use the function `identify_conditions()` to map conditions from intensity column names:

```{r message=FALSE, warning=FALSE}
condition <- identify_conditions(proteinGroups_Cbl,
                                  Column_intensity_pattern = "^Intensity.",
                                  split = "_", 
                                  bckg_pos = 1,
                                  time_pos = 2,
                                  bio_pos = 3,
                                  tech_pos = 4)
print(condition)
```

## Preprocess data


```{r message=FALSE, warning=FALSE}

preprocessed_data <- preprocess_data(proteinGroups_Cbl,
                            Column_gene_name = "Gene.names",
                            Column_score = "Score",
                            Column_ID = "Protein.IDs",
                            Column_Npep = NULL,
                            Column_intensity_pattern = "^Intensity.",
                            bait_gene_name = "Cbl",
                            condition = condition,
                            bckg_bait = "Cbl",
                            bckg_ctrl = "WT"
                            )

```

## Run `InteRact`

Replace missing values with methode `method`, compare protein intensities between bait and control backgrounds (`bckg_bait` and `bckg_ctrl` respectively) across experimental conditions:

```{r message=TRUE, warning=FALSE}
res <- InteRact(preprocess_df = preprocessed_data, 
                method = "none",
                pool_background = TRUE)
```

## Identify specific interactions

Identify prey proteins specifically enriched in the bait background :
```{r message=TRUE, warning=FALSE}
res <- identify_interactors(res, 
                            p_val_thresh = 0.001, 
                            fold_change_thresh = 3, 
                            n_success_min = 2, 
                            consecutive_success = TRUE)
names(res)
```

```{r message=TRUE, warning=FALSE}
print(res$interactor)
```

## Summarize results

Create a summary data.frame :
```{r}
#Create a summary data frame
sum_tbl <- summary_table(res)
head(sum_tbl[, 1:10])
```

## Volcano plots

Generate volcano plots :
```{r message=TRUE, warning=FALSE}
plot_volcanos(res, 
              conditions = "030", 
              p_val_thresh = 0.005, fold_change_thresh = 3)

```


## Recruitment kinetics

Plot kinetics of recruitment:
```{r message=TRUE, warning=FALSE, fig.width=3.5, fig.height=6 }
plot_per_condition(res)
```


## Focus on a protein

Compare protein intensities across condition for a given protein
```{r message=TRUE, warning=FALSE}
plot_comparison(res, names = "Crkl")
```