---
title: "Metadata"
date: "`r format(Sys.time(), '%Y - %m - %d')`"
output: 
  html_document:
    toc: true
    toc_float:
      toc_collapsed: false
vignette: >
  %\VignetteEngine{knitr::knitr}
  %\VignetteIndexEntry{Metadata}
  %\usepackage[UTF-8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(InteRact)
data("proteinGroups_Cbl")
```

## Generate metadata from column names

In the example dataset `proteinGroups_Cbl`, protein intensities are found in data columns whose names start with "Intensity".
We identify such columns using `grep()`

```{r message=FALSE, warning=FALSE}
idx_intensity_columns <- grep("^Intensity.", names(proteinGroups_Cbl))
print(names(proteinGroups_Cbl)[idx_intensity_columns][1:10])
```

Intensity columns are usually named using a pattern. Here the names of the cell type, of the experimental condition (time of stimulation), of the biological replicate and of the technical replicate are separated by the character `_`. We can use the function `identify_conditions()` to map conditions from intensity column names:

```{r message=FALSE, warning=FALSE}
condition <- identify_conditions(proteinGroups_Cbl,
                                  Column_intensity_pattern = "^Intensity.",
                                  split = "_", 
                                  bckg_pos = 1,
                                  time_pos = 2,
                                  bio_pos = 3,
                                  tech_pos = 4)
summary(condition)
```

## Import custom metadata

You can also import this metadata from a separate file. The package comes with one such file.

```{r message=FALSE, warning=FALSE}
condition_custom <- read.csv( system.file("extdata", "proteinGroups_Cbl_metadata.csv", package = "InteRact") )
summary(condition_custom)
```

This is the right place to reorder conditions if needed:

```{r message=FALSE, warning=FALSE}
levels(condition_custom$Stim.time) <- c("t=0s", "t=030s", "t=120s", "t=300s", "t=600s") 
```

Finally, metadata column names must be changed to match those obtained by calling `identify_conditions()`.

```{r message=FALSE, warning=FALSE}
names(condition_custom) <- c("column", "bckg", "time", "bio", "tech")
condition_custom$bait <- "Cbl"
```
As documented for `identify_conditions()`, `column` contains intensity column names (as they appear when calling `names()`), `bait` is a user-defined name for the bait, `bckg` contains the identity of the cell type, `time` contains the name of the experimental condition, and `bio` and `rep` contain the names of the biological and technical replicate respectively.

This custom metadata can then be passed to `InteRact()`:

```{r message=TRUE, warning=FALSE}

res <- InteRact(proteinGroups_Cbl, 
                bait_gene_name = "Cbl", 
                condition = condition_custom, 
                bckg_bait = "CBL-OST",
                bckg_ctrl = "Wild-type")
```

Note that we had to change parameters `bckg_bait` and `bckg_ctrl` according to the values taken by `condition_custom$bckg`.
Custom names now appears in the interactome and in subsequent plots (as for instance in the title of volcano plots):

```{r message=TRUE, warning=FALSE}
print(res$conditions)
print(res$replicates)
```



```{r message=TRUE, warning=FALSE}
plot_volcanos(res, p_val_thresh = 0.005, fold_change_thresh = 3)[[1]]
```

